Non-word repetition in Yélî Dnye

### 2020-09-11 getting_frequency_corpus.Rmd
added corpus frequency analyses

```{r}
# get frequencies in raw_YEL
#note, you should have ran the code documented in get_freq_cor.Rmd

@@

wds[1:1000]

@@

for(i in 1:dim(correspondances)[1]) { #transform into unicharacter
  wds_uni=gsub(correspondances[i,1],correspondances[i,2],wds_uni,fixed=T,useBytes = T)
}
wds_uni[1:1000]

@@

>>>>

```{r token freq}
# get frequencies in raw_YEL

@@

#wds[1:1000]

@@

for(i in 1:dim(correspondances)[1]) { #transform into unicharacter
  wds_uni=gsub(correspondances[i,1],correspondances[i,2],wds_uni,fixed=T,useBytes = T)
}
#wds_uni[1:1000]

correspondances2=correspondances
colnames(correspondances2)<-c("ortho","fake")
correspondances2=data.frame(correspondances2)
correspondances2$fake=gsub(" ","",as.character(correspondances2$fake))

#backtranslate
merge(counts,correspondances2,by.x="wds_uni",by.y="fake")->counts
counts=counts[order(counts$Freq),]

```{r type freq}

#initialize the unichar phono-like representation
wds_uni= names(table(wds))

for(i in 1:dim(correspondances)[1]) { #transform into unicharacter
  wds_uni=gsub(correspondances[i,1],correspondances[i,2],wds_uni,fixed=T,useBytes = T)
}
#wds_uni[1:1000]

@@

colnames(counts)[2]<-"counts_corpus_types"
counts$freq_corpus_types=counts$counts_corpus/sum(counts$counts_corpus)

write.table(counts,"segment-counts-types.txt",col.names = T,row.names = F,quote=T,sep="\t")
```

### 2020-09-11 manuscript.Rmd
added corpus frequency analyses

```{r xling-freq-ana}
xl_fr=glmer(correct~avg_fr+age.rounded+(1|file) + (1|target),data=trnsc,family="binomial")
mycoeff=round(summary(xl_fr)$coefficients,3)
```

We could include 885 observations (**why -- shouldn't it be 1k??**), from 41 children producing in any given trial one of 41 potential target words. The analysis revealed a significant estimate for the average cross-linguistic frequency of phones in the target words (ß = `r mycoeff["avg_fr","Estimate"]`, SE ß = `r mycoeff["avg_fr","Std. Error"]`, p = `r mycoeff["avg_fr","Pr(>|z|)"]`): Target words with phones found more frequently across languages had a higher proportion of words that were correctly repeated, as clear in Figure 2.

@@

@@

### Accuracy a function of item length

>>>>

```{r xling-freq-ana}
trnsc$avg_fr_s=scale(trnsc$avg_fr)
trnsc$age.rounded_s=scale(trnsc$age.rounded)
xl_fr=glmer(correct~avg_fr_s+age.rounded_s+(1|file) + (1|target),data=trnsc,family="binomial")
mycoeff=round(summary(xl_fr)$coefficients,3)
#summary(xl_fr)
#plot(xl_fr)
```

We could include 885 observations (**why -- shouldn't it be 1k??**), from 41 children producing in any given trial one of 41 potential target words. The analysis revealed a significant estimate for the average cross-linguistic frequency of phones in the target words (ß = `r mycoeff["avg_fr_s","Estimate"]`, SE ß = `r mycoeff["avg_fr_s","Std. Error"]`, p = `r mycoeff["avg_fr_s","Pr(>|z|)"]`): Target words with phones found more frequently across languages had a higher proportion of words that were correctly repeated, as clear in Figure 2. Age was also a significant predictor  (ß = `r mycoeff["age.rounded_s","Estimate"]`, SE ß = `r mycoeff["age.rounded_s","Std. Error"]`, p = `r mycoeff["age.rounded_s","Pr(>|z|)"]`).

@@

```{r cor vs xl}
#fr_cor=glmer(correct~avg_fr_cor+age.rounded+(1|file) + (1|target),data=trnsc,family="binomial")
#fr is not sig, but close (p=.1, estimate is 17)
#trnsc$avg_fr_cor_s=scale(trnsc$avg_fr_cor)
#both_fr=glmer(correct~avg_fr_s+avg_fr_cor_s+age.rounded_s+(1|file) + (1|target),data=trnsc,family="binomial")
#both_coeff=round(summary(both_fr)$coefficients,3)

#fr_cor_ty=glmer(correct~avg_fr_cor_ty+age.rounded+(1|file) + (1|target),data=trnsc,family="binomial")
#fr is sig
trnsc$avg_fr_cor_ty_s=scale(trnsc$avg_fr_cor_ty)
both_fr=glmer(correct~avg_fr_s+avg_fr_cor_ty_s+age.rounded_s+(1|file) + (1|target),data=trnsc,family="binomial")
both_coeff=round(summary(both_fr)$coefficients,3)

read.delim("segments_with_cor_freq.txt", encoding="UTF-8")->segments
freq_cor=cor.test(segments$pc,log(segments$freq_corpus_types))
```

We next checked whether this may actually be due to frequency of the sounds within the language. We estimated frequency of the phones present in the stimuli in a corpus of child-centered recordings [@casillas2020png], and applied the natural logarithm. As before, unattested sounds were not considered (i.e., they were declared NA so that they do not count for analyses). Phone frequency estimated from this corpus were correlated with cross-linguistic phone frequencies (r(`r freq_cor$parameter`)=`r round(freq_cor$estimate,3)`, =`r round(freq_cor$p.value,3)`). Therefore, we fit another mixed logistic regression, this time declaring as fixed effects scaled cross-linguistic and corpus frequencies (averaged across all attested phones within each stimulus item), in addition to age. As before, the model contained random slopes for both child ID and target. In this model, both cross-linguistic frequency (ß = `r both_coeff["avg_fr_s","Estimate"]`, SE ß = `r both_coeff["avg_fr_s","Std. Error"]`, p = `r both_coeff["avg_fr_s","Pr(>|z|)"]`) and age (ß = `r both_coeff["age.rounded_s","Estimate"]`, SE ß = `r both_coeff["age.rounded_s","Std. Error"]`, p = `r both_coeff["age.rounded_s","Pr(>|z|)"]`) were significant predictors of accuracy, but corpus frequency (ß = `r both_coeff["avg_fr_cor_ty_s","Estimate"]`, SE ß = `r both_coeff["avg_fr_cor_ty_s","Std. Error"]`, p = `r both_coeff["avg_fr_cor_ty_s","Pr(>|z|)"]`) was not.

<!-- a2m should we point out that the coefficient for cross-ling frequency is reduced from .77 to .67, so indirectly corpus frequency does affect a little bit? Or making things too complicated, and just say "so corpus frequency does not explain away these results" -->

@@

### Accuracy as a function of item length
